---
format:
  # html: default
  typst:
    template-partials:
      - typst-template.typ
      - typst-show.typ
    keep-typ: true
cv-name: "Leonhard Kestel"
cv-email: "leo.kestel@lmu.de"
#cv-phone: "555-123-4567"
cv-url: "leokestel.de"
cv-orcid: "0009-0008-4549-4960"
cv-github: "kestelnadomu"
#cv-address: "Room 255, 1400 University Ave., City, ST 12345"
cv-date: "August 2026"
execute:
  echo: false
  warning: false
  fig-keep: none
---


```{r}
#| label: setup

if (!interactive()) {
  pdf(NULL)  # Prevent graphics device errors in non-interactive mode
}

library(yaml)

# Load all data files
experience <- yaml::read_yaml("data/experience.yml")
education <- yaml::read_yaml("data/education.yml")
grants <- yaml::read_yaml("data/grants.yml")
teaching <- yaml::read_yaml("data/teaching.yml")
projects <- yaml::read_yaml("data/projects.yml")
honors <- yaml::read_yaml("data/honors.yml")
presentations <- yaml::read_yaml("data/presentations.yml")
service <- yaml::read_yaml("data/service.yml")
extracurricular <- yaml::read_yaml("data/extracurricular.yml")
```

<!-- Research Interests (compact) -->

```{=typst}
// #cv-section("Research Interests")

// #text(font: "Source Sans 3", size: 9.5pt, fill: color-gray)[
//   Short summary...
// ]

// #cv-subsection("Keywords")

#text(font: "Source Sans 3", weight: "bold", size: 9.5pt, fill: color-darkgray)[Keywords:]
#text(font: "Source Sans 3", size: 9.5pt, fill: color-lightgray)[
  Algorithmic Fairness #sym.dot.c
  Neurosymbolic AI #sym.dot.c
  Causal Aware Machine Learning #sym.dot.c
  Data Science for the Public Sector
]
```

<!-- Academic Appointments -->

```{=typst}
#cv-section("Experience")
```

```{r}
#| output: asis
for (a in experience) {
  cat(sprintf(
    '```{=typst}\n#cv-entry(\n  institution: "%s",\n  department: "%s",\n  location: "%s",\n  title: "%s",\n  date: "%s",\n)\n```\n\n',
    a$institution, a$department, a$location, a$title, a$date
  ))
}
```

<!-- Projects -->

```{=typst}
#cv-section("Applied Projects")
```

```{r}
#| output: asis
for (t in projects) {
  cat(sprintf(
    '```{=typst}\n#cv-subsection("%s")\n```\n\n',
    t$institution
  ))
  for (c in t$projects) {
    cat(sprintf(
      '```{=typst}\n#project-entry(project: "%s", role: "%s", date: "%s", href: "%s")\n```\n\n',
      c$project, c$role, c$date, c$href %||% ""
    ))
  }
}
```

<!-- Education -->

```{=typst}
#cv-section("Education")
```

```{r}
#| output: asis
for (e in education) {
  details_str <- if (!is.null(e$details) && e$details != "") {
    gsub('\n', ' ', trimws(e$details))
  } else {
    ""
  }
  # Escape quotes for Typst
  details_str <- gsub('"', '\\\\"', details_str)

  if (details_str != "") {
    cat(sprintf(
      '```{=typst}\n#edu-entry(\n  institution: "%s",\n  department: "%s",\n  degree: "%s",\n  date: "%s",\n  details: [%s],\n)\n```\n\n',
      e$institution, e$department %||% "", e$degree, e$date, details_str
    ))
  } else {
    cat(sprintf(
      '```{=typst}\n#edu-entry(\n  institution: "%s",\n  department: "%s",\n  degree: "%s",\n  date: "%s",\n)\n```\n\n',
      e$institution, e$department %||% "", e$degree, e$date
    ))
  }
}
```

<!-- Peer-Reviewed Publications -->

```{=typst}
#cv-section("Publications")
```

```{r}
#| output: asis

# Read and parse BibTeX manually for full control
bib_lines <- readLines("publications.bib")

# Simple BibTeX parser
parse_bib <- function(lines) {
  entries <- list()
  current <- NULL
  brace_depth <- 0

  for (line in lines) {
    # Start of entry
    if (grepl("^@", line)) {
      if (!is.null(current)) entries <- c(entries, list(current))
      current <- list(raw = "", type = sub("^@(\\w+)\\{.*", "\\1", line),
                       key = sub("^@\\w+\\{([^,]+),.*", "\\1", line))
      current$raw <- line
      brace_depth <- nchar(gsub("[^{]", "", line)) - nchar(gsub("[^}]", "", line))
      next
    }

    if (!is.null(current)) {
      current$raw <- paste0(current$raw, "\n", line)
      brace_depth <- brace_depth + nchar(gsub("[^{]", "", line)) - nchar(gsub("[^}]", "", line))

      # Parse fields
      if (grepl("^\\s*\\w+\\s*=", line)) {
        field <- trimws(sub("^\\s*(\\w+)\\s*=.*", "\\1", line))
        value <- trimws(sub("^\\s*\\w+\\s*=\\s*", "", line))
        value <- gsub("[{}\"']", "", value)
        value <- sub(",\\s*$", "", value)  # strip trailing comma only
        value <- trimws(value)
        current[[field]] <- value
      }

      if (brace_depth <= 0) {
        entries <- c(entries, list(current))
        current <- NULL
      }
    }
  }
  if (!is.null(current)) entries <- c(entries, list(current))
  entries
}

entries <- parse_bib(bib_lines)

# Format authors: "Last, F." style, bold your name
# CUSTOMIZE: Change "Author" to your last name
format_authors <- function(author_str) {
  # Split by " and "
  authors <- trimws(strsplit(author_str, "\\s+and\\s+")[[1]])

  formatted <- sapply(authors, function(a) {
    # Handle team names (no comma = not "Last, First" format)
    if (!grepl(",", a)) return(a)

    parts <- trimws(strsplit(a, ",")[[1]])
    last <- parts[1]
    first <- parts[2]
    # Take first letter of first name
    initial <- substr(trimws(first), 1, 1)

    # CUSTOMIZE: Change "Author" to your last name to bold it
    if (grepl("Author", last, ignore.case = TRUE)) {
      sprintf("*%s, %s.*", last, initial)
    } else {
      sprintf("%s, %s.", last, initial)
    }
  }, USE.NAMES = FALSE)

  paste(formatted, collapse = ", ")
}

# Under review FIRST (before journal articles)
under_review <- Filter(function(e) !is.null(e$keywords) && grepl("under-review", e$keywords), entries)
under_review <- under_review[order(sapply(under_review, function(e) -as.numeric(e$year %||% "0")))]

if (length(under_review) > 0) {
  cat('```{=typst}\n#cv-subsection("Under Review")\n```\n\n')

  for (p in under_review) {
    authors <- format_authors(p$author %||% "")
    title <- p$title %||% ""
    journal <- p$journal %||% ""
    note <- p$note %||% ""

    cite <- sprintf('%s, "%s"', authors, title)
    if (note != "") cite <- sprintf("%s (%s at *%s*)", cite, tolower(note), journal)

    cat(sprintf(
      '```{=typst}\n#pub-entry([%s], date: "---")\n```\n\n',
      cite
    ))
  }
}

```

<!-- Journal Articles (published) -->

```{r}
#| output: asis

# Re-parse for journal articles section
bib_lines2 <- readLines("publications.bib")
entries2 <- parse_bib(bib_lines2)

published <- Filter(function(e) !is.null(e$keywords) && grepl("published", e$keywords), entries2)
published <- published[order(sapply(published, function(e) -as.numeric(e$year %||% "0")))]

cat('```{=typst}\n#cv-subsection("Published Articles")\n```\n\n')

for (p in published) {
  authors <- format_authors(p$author %||% "")
  title <- p$title %||% ""
  journal <- p$journal %||% ""
  year <- p$year %||% ""
  vol <- p$volume %||% ""
  pages <- p$pages %||% ""
  doi <- p$doi %||% ""

  cite <- sprintf('%s (%s). "%s."', authors, year, title)
  if (journal != "") cite <- sprintf("%s *%s*", cite, journal)
  if (vol != "") cite <- sprintf("%s, %s", cite, vol)
  if (pages != "") cite <- sprintf("%s: %s", cite, pages)
  cite <- paste0(cite, ".")
  if (doi != "") cite <- sprintf('%s doi: #link("https://doi.org/%s")[%s]', cite, doi, doi)

  cat(sprintf(
    '```{=typst}\n#pub-entry([%s], date: "%s")\n```\n\n',
    cite, year
  ))
}
```

<!-- Grants -->

<!-- ```{=typst}
#cv-section("Grants")
``` -->

```{r}
#| output: asis

render_grants <- function(grant_list, subsection_title) {
  if (length(grant_list) == 0) return(invisible())
  cat(sprintf('```{=typst}\n#cv-subsection("%s")\n```\n\n', subsection_title))

  for (g in grant_list) {
    project <- gsub('"', '\\\\"', g$project %||% "")
    cat(sprintf(
      '```{=typst}\n#grant-entry(\n  title: "%s",\n  funder: "%s",\n  role: "%s",\n  amount: "%s",\n  date: "%s",\n  description: "%s",\n)\n```\n\n',
      g$title, project, g$role %||% "", g$amount %||% "", g$date %||% "", g$description %||% ""
    ))
  }
}

render_grants(grants$funded, "Funded")
render_grants(grants$submitted, "Submitted (Under Review)")
render_grants(grants$in_preparation, "In Preparation")
render_grants(grants$completed, "Completed")
render_grants(grants$not_funded, "Not Funded")
```

<!-- Teaching -->

```{=typst}
#cv-section("Teaching")
```

```{r}
#| output: asis
for (t in teaching) {
  cat(sprintf(
    '```{=typst}\n#cv-subsection("%s")\n```\n\n',
    t$institution
  ))
  for (c in t$courses) {
    cat(sprintf(
      '```{=typst}\n#teaching-entry(course: "%s", role: "%s", semesters: "%s")\n```\n\n',
      c$course, c$role, c$semesters
    ))
  }
}
```


<!-- Presentations -->

<!-- ```{=typst}
#cv-section("Presentations")
``` -->

```{r}
#| output: asis

render_presentations <- function(pres_list, subsection_title) {
  if (length(pres_list) == 0) return(invisible())
  cat(sprintf('```{=typst}\n#cv-subsection("%s")\n```\n\n', subsection_title))

  for (p in pres_list) {
    authors <- p$authors %||% ""
    title <- gsub('"', '\\\\"', p$title %||% "")
    venue <- gsub('"', '\\\\"', p$venue %||% "")
    date <- p$date %||% ""

    # CUSTOMIZE: Change "Author, Y." to match your abbreviated name
    authors <- gsub("Author, Y\\.", "*Author, Y.*", authors)

    content <- sprintf('%s "%s." %s.', authors, title, venue)

    cat(sprintf(
      '```{=typst}\n#presentation-entry([%s], date: "%s")\n```\n\n',
      content, date
    ))
  }
}

render_presentations(presentations$invited, "Invited Talks")
render_presentations(presentations$conference, "Conference Presentations")
```

<!-- Workshop Participation -->

<!-- ```{=typst}
#cv-subsection("Workshop Participation")
```

```{r}
#| output: asis
for (w in presentations$workshops) {
  title <- gsub('"', '\\\\"', w$title %||% "")
  venue <- gsub('"', '\\\\"', w$venue %||% "")
  cat(sprintf(
    '```{=typst}\n#presentation-entry([*%s.* %s.], date: "%s")\n```\n\n',
    title, venue, w$date %||% ""
  ))
}
```

<!-- Honors, Awards & Fellowships -->

```{=typst}
#cv-section("Honors & Fellowships")
```

```{r}
#| output: asis

# cat('```{=typst}\n#cv-subsection("Fellowships")\n```\n\n')

for (f in honors$fellowships) {
  amount_str <- if (!is.null(f$amount) && f$amount != "") sprintf(" (%s)", f$amount) else ""
  cat(sprintf(
    '```{=typst}\n#service-entry(role: "%s", organization: "%s%s", date: "%s")\n```\n\n',
    f$title, f$organization, amount_str, f$date %||% ""
  ))
}

# cat('```{=typst}\n#cv-subsection("Awards & Research Support")\n```\n\n')

# for (a in honors$awards) {
#   amount_str <- if (!is.null(a$amount) && a$amount != "") a$amount else ""
#   cat(sprintf(
#     '```{=typst}\n#service-entry(role: "%s", organization: "%s", date: "%s")\n```\n\n',
#     a$title, paste0(a$organization, if (amount_str != "") paste0(", ", amount_str) else ""),
#     a$date %||% ""
#   ))
# }
```

<!-- Service -->

<!-- ```{=typst}
#cv-section("Service")
``` -->

```{r}
#| output: asis

# # Department / University
# cat('```{=typst}\n#cv-subsection("Department & University")\n```\n\n')
# for (s in service$department_university) {
#   cat(sprintf(
#     '```{=typst}\n#service-entry(role: "%s", organization: "%s", date: "%s")\n```\n\n',
#     s$role, s$organization, s$date %||% ""
#   ))
# }

# # Mentoring
# cat('```{=typst}\n#cv-subsection("Mentoring")\n```\n\n')
# for (m in service$mentoring) {
#   details_str <- if (!is.null(m$details) && m$details != "") paste0(" ", m$details) else ""
#   cat(sprintf(
#     '```{=typst}\n#service-entry(role: "%s", organization: "%s%s", date: "%s")\n```\n\n',
#     m$role, m$organization, details_str, m$date %||% ""
#   ))
# }

# # Student Advising
# cat('```{=typst}\n#cv-subsection("Student Advising")\n```\n\n')
# students <- paste(service$student_advising, collapse = " #sym.dot.c ")
# cat(sprintf('```{=typst}\n#cv-item([%s])\n```\n\n', students))

# # Ad-Hoc Reviewing
# cat('```{=typst}\n#cv-subsection("Ad-Hoc Reviewer")\n```\n\n')
# journals <- paste(paste0("_", service$reviewing, "_"), collapse = "; ")
# cat(sprintf('```{=typst}\n#cv-item([%s])\n```\n\n', journals))

# # Abstract Reviewing
# cat('```{=typst}\n#cv-subsection("Abstract Reviewer")\n```\n\n')
# abstracts <- paste(service$abstract_reviewing, collapse = "; ")
# cat(sprintf('```{=typst}\n#cv-item([%s])\n```\n\n', abstracts))

# # Professional Organizations
# cat('```{=typst}\n#cv-subsection("Professional Organizations")\n```\n\n')
# for (o in service$memberships) {
#   cat(sprintf(
#     '```{=typst}\n#service-entry(role: "%s", organization: "%s", date: "%s")\n```\n\n',
#     o$role, o$organization, o$date %||% ""
#   ))
# }
```

<!-- Extracurricular -->

```{=typst}
#cv-section("Extracurricular")
```

```{r}
#| output: asis
for (e in extracurricular) {
  cat(sprintf(
    '```{=typst}\n#extracurricular-entry(date: "%s", institution: "%s", role: "%s", location: "%s")\n```\n\n',
    e$date, e$institution, e$role, e$location
  ))
}
```